This is an example of article title

### 2021-09-27 paper/paper.tex

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb|\ref|) in order to
protect against late changes of order, etc.

@@

If the file \verb|juliacon.cls| is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb|juliacon| document class is implemented
as a complete class, not a document style option. In order to
use the \verb|juliacon| document class, replace \verb|article| by \verb|juliacon| in the
\verb|\documentclass| command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb|\documentclass{article}| \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb|\documentclass{juliacon}| \vskip 6pt
In general, the following standard document \verb|style| options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb|10pt,| \verb|11pt,| \verb|12pt| ? unavailable;
\item[(2)] \verb|twoside| (no associated style file) ? \verb|twoside| is the default;
\item[(3)] \verb|fleqn,|\verb|leqno,|\verb|titlepage|? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb|juliacon| class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
\verb|\def| and \verb|\newcommand| commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb|\juliacon.cls| as early as possible in the creation of their files.

@@

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb|\includegraphics| command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb|\label| and \verb|\ref|  commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb|Figure~\ref{sample-figure}| \subsection{Tables}
\label{subsub:sec_Tab}
The \verb|juliacon| class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}\end{verbatim}

>>>>

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb|\ref| ) in order to
protect against late changes of order, etc.

@@

If the file \verb|juliacon.cls|  is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb|juliacon|  document class is implemented
as a complete class, not a document style option. In order to
use the \verb|juliacon  document class, replace \verb|article|  by \verb|juliacon|  in the
\verb|\documentclass|  command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb|\documentclass{article}|  \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb|\documentclass{juliacon}|  \vskip 6pt
In general, the following standard document \verb|style|  options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb|10pt|,  \verb|11pt|,  \verb|12pt|   ? unavailable;
\item[(2)] \verb|twoside|  (no associated style file) ? \verb|twoside|  is the default;
\item[(3)] \verb|fleqn|, \verb|leqno|, \verb|titlepage| ? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb|juliacon|  class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
\verb|\def|  and \verb|\newcommand|   commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb|juliacon.cls|  as early as possible in the creation of their files.

@@

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb|\includegraphics|   command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb|\label|  and \verb|\ref|   commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb|Figure~\ref{sample-figure}|

 \subsection{Tables}
\label{subsub:sec_Tab}
The \verb|juliacon|   class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\end{verbatim}
